\documentclass[12pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{booktabs}
\usepackage{xcolor,colortbl}
\usepackage{pstricks}
\usepackage{eurosym} 
\usepackage{longtable}
\usepackage{blindtext}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{pdfpages}
\usepackage{tabularx} 
\usepackage{transparent}
\usepackage{array}
\usepackage{etoolbox}
\usepackage{float}
\usepackage{lscape}

\author{Communications Department}
\title{Organization}
\begin{document}
\maketitle
\section{Scope}
At the Project Charter the scopte of our department was fixed to the following items.
\begin{itemize}
\item An analysis will be done to clarify how many ground stations must operate and the possibility of placing a central one in UPC ESEIAAT.
\item The requirements and costs of the ground station will be determined. 
\item Communication logistics will be defined.
\item Communication logistics will be defined. Thus, how the satellites decide whether to send the data or to store it, and if they are to send, where they should do it, is going to be approached. In other words, a high level communications protocol is going to be defined. 
\end{itemize}
\section{Tasks}
In the project charter we had 3 major tasks. It is needed to divide these tasks into more detailed tasks so a proper following of the project could be done. 
\paragraph{Communication protocol}
The communication protocol taks lasts 100 hours. It can be divided into: 
\begin{itemize}
\item Physical topology of the constellation: 15 hours.
\item Working frequency: 10 hours.
\item Communication logistics definition: 20 hours.
\item Study of existing protocols: 25 hours.
\item Protocol definition (by creating it or adapting and existing one): 30 hours.
\end{itemize}
\paragraph{Ground station}
This part will take 80 hours. It is composed by the following tasks:
\begin{itemize}
\item Number of Ground Station required: 20 hours.
\item Systems (antenna) needed: 40 hours.
\item Estimation of the cost: 20 hours.
\end{itemize}
\end{document}